---
title: "Introduction to seor"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to seor}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`seor` is a *metapackage*: it bundles a suite of focused SEO and web-developer
packages so you can install and load them in one step, the same way the
`tidyverse` package works.

```{r setup}
library(seor)
```

Attaching `seor` puts every member package on the search path. The members are:

```{r}
seor_packages()
```

| Package     | Purpose                                        |
|-------------|------------------------------------------------|
| `rurl`      | URL parsing and manipulation                   |
| `punycoder` | Punycode / internationalized-domain conversion |
| `pslr`      | Public Suffix List lookups                     |
| `sitemapr`  | XML sitemap parsing                            |
| `pagerankr` | PageRank estimation                            |

`robotstxtr` is a planned member; once it is installed, `library(seor)` attaches
it automatically alongside the core packages.

If two attached packages export the same name, `seor_conflicts()` reports which
package wins on the search path:

```{r}
seor_conflicts()
```
